Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-10 vesicle_code/docs/permeableVes/main.tex
yny

We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
$Ca_E=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
$\dot{\gamma}$ is the shear rate of the planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
 %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
 When $\beta=0$ (impermeable
case), a vesicle's reduced area and viscosity contrast determine whether
it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
viscosity contrast, we find that a semipermeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics, similar to the
case of an impermeable vesicle.

@@

For a variety of semipermeability rates and flow rates, a semipermeable
vesicle reaches a steady equilibrium as in
Figure~\ref{fig:shearComposite}(a). Since the final shape is independent
of the initial reduced area, we initialize the vesicle with reduced area
$\alpha = 0.65$ for all simulations in
Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
vesicle shape and its reduced area. We see that the flow rate
significantly affects the final vesicle shape, but the semipermeability
rate has a minor effect. Instead, as we saw in the quiescent analysis,
$\beta$ sets a time scale since the time required for a vesicle to reach
its steady state configuration is proportional to $\beta^{-1}$.

>>>>

We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
$\dot{\gamma}$ is the shear rate of the planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
 %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
 When $\beta=0$ (impermeable
case), a vesicle's reduced area and viscosity contrast determine whether
it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
viscosity contrast, we find that a semipermeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics, similar to the
case of an impermeable vesicle.

@@

For a variety of semipermeability rates and $Ca_\mathrm{E}$, a semipermeable
vesicle reaches a steady equilibrium as in
Figure~\ref{fig:shearComposite}(a). Since the final shape is independent
of the initial reduced area, we initialize the vesicle with reduced area
$\alpha = 0.65$ for all simulations in
Figure~\ref{fig:shearComposite}(b), where we summarize the steady state
vesicle shape and its reduced area. We see that the capillary number (flow rate)
significantly affects the final vesicle shape, but the semipermeability
rate has a minor effect. Instead, as we saw in the quiescent analysis,
$\beta$ sets a time scale since the time required for a vesicle to reach
its steady state configuration is proportional to $\beta^{-1}$.
